%!TEX TS-program = xelatex
% !TEX root = ../thesis.tex
% Do not delete; used to set build system
% the acknowledgments section

I would like to thank my advisors Professor Xiao-Li Meng and Professor Edoardo Airoldi first and foremost.
Both have been incredibly supportive mentors and collaborators throughout my graduate studies.
I have been continually amazed by the depth and breadth of Xiao-Li's knowledge and scholarship, and it has been a wonderful privilege to work with him over the past five years.
I will endeavor to keep seeking out the subtleties of statistics, as he has shown me.
Edo has been an invaluable guide to the worlds of networks, machine learning, and computational biology, as well as a coauthor, a collaborator, and a friend.

I would also like to thank the entire faculty of the Department of Statistics for their support and wisdom.
They created a wonderful intellectual environment both inside and outside of the classroom that I was very lucky be a part of for a few years.
The courses I took with Joe Blitzstein, Carl Morris, Jun Liu, and Don Rubin opened my eyes to the world of statistics beyond my original training in econometrics.
Everyone I have taught with over the past five years has also helped me to grow and take on challenges I never expected to, for which I thank them.
I would also like to particularly thank Jun Liu for becoming a reader for this dissertation late in the process.

Collaborative research has been at the heart of my graduate career, and I would like to extend my thanks everyone I have worked with.
Xu Zhou and Erin O'Shea have provided invaluable scientific guidance and perspective on my nucleosome research.
On my proteomics research, Eric Sol\'is, David Allan Drummond, and Bogdan Budnik have been excellent guides to the technically challenging world of mass spectrometry.
Throughout my time at Harvard, the CHASC group has provided a stimulating research environment and valuable feedback.

My colleagues have been a source of advice and inspiration throughout my time at Harvard.
I thank all of you for your patience as we worked through theoretical and computational problems and for all of the wonderful times we had throughput my studies at Harvard.

I would also like to thank my mother Kelley Weaver for her support through everything.
Last but certainly not least, thank you to my wonderful fianc\'ee Paula Griffin.
This dissertation would not have been possible without her patience and support.
